### 2017-01-06 paper/evaluation.tex
updating rq1

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server). \Fix{Describe CPU isolation}

@@

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). A previous work used a similar categorization
except for the \emph{medium} group \cite{gligoric-etal-issta2015}.  We
added a new group because \Fix{justify or use the same
classification}.  Figure~\ref{fig:piechart-time} shows the proportion
of subjects per group and Figure~\ref{fig:boxplots-time} shows the
distribution of elapsed time for each group (boxplots).

\Jbc{I will rework the results and plots}

\begin{figure}[h!]
    \centering
    \begin{minipage}{2in}%
    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
    \end{minipage}%
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).}
\end{figure}

>>>>

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
To avoid noise from OS events, we executed this experiment in our
dedicated server remotely via SSH with the operating system running
only essential services (\eg, the SSH server). \Fix{Describe CPU
isolation}.

@@

We grouped the subjects according the execution time (in average)
using the same criteria of a previous work
\cite{gligoric-etal-issta2015}: subjects that run in less than one
minute were classified as \emph{short execution} and \emph{long
execution} otherwise. Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group and figure~\ref{fig:boxplots-time}
shows the distribution of elapsed time for each group (boxplots).

\begin{figure}[h!]
    \centering
    \begin{minipage}{2in}%
    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
    \end{minipage}%
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$) and long
    execution ($1m \leq t$).}
\end{figure}
